\documentclass{article}
\usepackage{amsmath, amssymb, fullpage}

\title{Precalculus Vector Test}
\date{}

\begin{document}
\maketitle

\section*{Instructions}
Complete all questions on your own paper. Show all work for full credit. Answers without supporting work will receive no credit.

\section*{Basic Vector Addition}
\begin{enumerate}
    \item Given vectors $\vec{a} = 3\hat{i} + 4\hat{j}$ and $\vec{b} = -1\hat{i} + 2\hat{j}$, find the vector sum $\vec{a} + \vec{b}$.
    \item If $\vec{c} = 5\hat{i} - 3\hat{j}$ and $\vec{d} = 2\hat{i} + 6\hat{j}$, calculate $\vec{c} + \vec{d}$.
\end{enumerate}

\section*{Resolving Vectors into Components}
\begin{enumerate}
    \setcounter{enumi}{2}
    \item Resolve the vector $\vec{e} = 7\hat{i} - 7\sqrt{3}\hat{j}$ into its magnitude and direction.
    \item For vector $\vec{f} = 12\cos(60^\circ)\hat{i} + 12\sin(60^\circ)\hat{j}$, find its rectangular components.
\end{enumerate}

\section*{Converting Between Rectangular and Polar Notation}
\begin{enumerate}
    \setcounter{enumi}{4}
    \item Convert the vector $\vec{g} = 4\hat{i} + 3\hat{j}$ to polar notation.
    \item Convert the vector given in polar form $R = 10, \theta = 45^\circ$ to rectangular notation.
\end{enumerate}

\section*{Magnitude of Vectors}
\begin{enumerate}
    \setcounter{enumi}{6}
    \item Find the magnitude of $\vec{h} = -6\hat{i} + 8\hat{j}$.
    \item Calculate the magnitude of $\vec{i} = 9\hat{i} - 12\hat{j}$.
\end{enumerate}

\section*{Unit Vectors}
\begin{enumerate}
    \setcounter{enumi}{8}
    \item Find the unit vector in the direction of $\vec{j} = 3\hat{i} - 4\hat{j}$.
    \item Determine the unit vector of $\vec{k} = \sqrt{2}\hat{i} + \sqrt{2}\hat{j}$.
\end{enumerate}

\section*{Word Problems}
\begin{enumerate}
    \setcounter{enumi}{10}
    \item A plane flies 300 km east and then 400 km south. Represent the plane's displacement as a vector in rectangular notation and find its magnitude.
    \item A river flows with a current of 5 km/h in the east direction. A boat wants to reach a point directly across the river, north of its current position, which is 10 km away. If the boat can travel at 10 km/h relative to the water, find the actual velocity of the boat in rectangular form.
    \item A person walks 8 km, 60 degrees north of east, and then walks 6 km east. Find the total displacement vector in both rectangular and polar forms.
\end{enumerate}

\end{document}
