\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[version=4]{mhchem}
\usepackage{stmaryrd}

\title{Day 3: Parametric Equations Free Response }

\author{}
\date{}


\begin{document}
\maketitle
\section*{1. Calculator Active - \#2 on 2012 BC Exam}
For $t \geq 0$, a particle is moving along a curve so that its position at time $t$ is $(x(t), y(t))$. At time $t=2$, the particle is at position $(1,5)$. It is known that $\frac{d x}{d t}=\frac{\sqrt{t+2}}{e^{t}}$ and $\frac{d y}{d t}=\sin ^{2} t$.

(a) Is the horizontal movement of the particle to the left or to the right at time $t=2$ ? Explain your answer. Find the slope of the path of the particle at time $t=2$.

(b) Find the $x$-coordinate of the particle's positions at time $t=4$.

(c) Find the speed of the particle at time $t=4$. Find the acceleration vector of the particle at time $t=4$.

(d) Find the distance traveled by the particle from $t=2$ to $t=4$.

\section*{2. Calculator Active - \#1 on 2011 BC Exam}
At time $t$, a particle moving in the $x y$-plane is at position $(x(t), y(t))$, where $x(t)$ and $y(t)$ are not explicitly given. For $t \geq 0, \frac{d x}{d t}=4 t+1$ and $\frac{d y}{d t}=\sin \left(t^{2}\right)$. At time $t=0, x(0)=0$ and $y(0)=-4$.

(a) Find the speed of the particle at time $t=3$, and find the acceleration vector of the particle at time $t=3$.

(b) Find the slope of the line tangent to the path of the particle at time $t=3$.

(c) Find the position of the particle at time $t=3$.

(d) Find the total distance traveled by the particle over the time interval $0 \leq t \leq 3$.

\section*{3. Calculator Active - \#3 on 2010 BC Exam}
A particle is moving along a curve so that its position at time $t$ is $(x(t), y(t))$, where $x(t)=t^{2}-4 t+8$ and $y(t)$ is not explicitly given. Both $x$ and $y$ are measured in meters, and $t$ is measured in seconds. It is known that $\frac{d y}{d t}=t e^{t-3}-1$.

(a) Find the speed of the particle at time $t=3$ seconds.

(b) Find the total distance traveled by the particle for $0 \leq t \leq 4$ seconds.

(c) Find the time $t, 0 \leq t \leq 4$, when the line tangent to the path of the particle is horizontal. Is the direction of motion of the particle toward the left or toward the right at that time? Give a reason for your answer.

(d) There is a point with $x$-coordinate 5 through which the particle passes twice. Find each of the following.

(i) The two values of $t$ when that occurs

(ii) The slopes of the lines tangent to the particle's path at that point

(iii) The $y$-coordinate of that point, given $y(2)=3+\frac{1}{e}$

\section*{4. Calculator Active - \#2 on 2010 BC Exam (Form B)}
The velocity vector of a particle moving in the $x y$-plane has components given by

$$
\frac{d x}{d t}=14 \cos \left(t^{2}\right) \sin \left(e^{t}\right) \text { and } \frac{d y}{d t}=1+2 \sin \left(t^{2}\right) \text {, for } 0 \leq t \leq 1.5 \text {. }
$$

At time $t=0$, the position of the particle is $(-2,3)$.

(a) For $0<t<1.5$, find all values of $t$ at which the line tangent to the path of the particle is vertical.

(b) Write an equation for the line tangent to the path of the particle at $t=1$.

(c) Find the speed of the particle at $t=1$.

(d) Find the acceleration vector of the particle at $t=1$.

\section*{5. Calculator Active - \#1 on 2008 BC Exam (Form B)}
A particle moving along a curve in the $x y$-plane has position $(x(t), y(t))$ at time $t \geq 0$ with

$$
\frac{d x}{d t}=\sqrt{3 t} \text { and } \frac{d y}{d t}=3 \cos \left(\frac{t^{2}}{2}\right)
$$

The particle is at position $(1,5)$ at time $t=4$.

(a) Find the acceleration vector at time $t=4$.

(b) Find the $y$-coordinate of the position of the particle at time $t=0$.

(c) On the interval $0 \leq t \leq 4$, at what time does the speed of the particle first reach 3.5 ?

(d) Find the total distance traveled by the particle over the time interval $0 \leq t \leq 4$.


\end{document}