% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{fullpage}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\author{}
\date{}

\begin{document}

\hypertarget{test-6-retake}{%
\section{Test 6 Retake}\label{test-6-retake}}
\pagestyle{empty}
Select appropriate problems (all the series is one option, the taylor
question, and the interval question are 2 other options) based on what
you missed on the first test.

\hypertarget{convergence-tests-3pts-each}{%
\subsection{Convergence Tests (3pts
each)}\label{convergence-tests-3pts-each}}

Prove convergence or divergence using appropriate tests. Show all
relevant work and give precise jusitifications

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setlength{\itemsep}{1.5in}
\item
  \(\displaystyle \sum_{n=1}^\infty \dfrac{n+1}{\sqrt{2n^3+1}}\)
\item
  \(\displaystyle \sum_{n=1}^\infty \dfrac{6}{2n+1}\)
\item
  \(\displaystyle \sum_{n=1}^\infty \dfrac{n!}{2^{2n+1}}\)
\item
  \(\displaystyle \sum_{n=1}^\infty n^2\dfrac{3}{2^n}\)
\end{enumerate}
\vspace{1.5in*}

For the following alternating series, additionally test for absolute
convergence (4pts).

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{4}
\tightlist
\item
  \(\displaystyle \sum_{n=1}^\infty (-1)^{n+1}\dfrac{\sqrt{n+1}}{3n!}\)
\end{enumerate}
\vspace{1.5in*}

\hypertarget{interval-of-convergence-4-pts}{%
\subsection{Interval of Convergence (4
pts)}\label{interval-of-convergence-4-pts}}

Give the interval of convergence for the following problem. You do not
need to test endpoints.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{5}
\tightlist
\item
  \(\displaystyle \sum_{n=1}^{\infty} \frac{(-1)^n (2x-1)^n}{n^3}\)
\end{enumerate}
\vspace{2.5in*}

\hypertarget{taylor-series-4-pts}{%
\subsection{Taylor Series (4 pts)}\label{taylor-series-4-pts}}

Write the Maclaurin Series for \(f(x) = 3+2x\cos(3x^2)\), stopping after
the 4th term. Your answer must use transformations from a known series.

\end{document}
